The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-08-13 Paper.Rmd
modified

Though a few examples have been found which shows copula approach to model dependencies in bioinformatics [@Kim2008], medical research [@Emura2016] or a short period study of intersite dependence of rainfall data [@Serinaldi2008], the multivariate copula approach still, we believe, remains unexplored in ecology or related field and thus have potential scope to better capture the evolution of ecological time series data. So, in ecological perspective, when we find a dominantly lower (upper) tail dependence structure, it means both variable are rare synchronously. If any one of them be environmental variable and the other is an observable (like abundance of a species) then it can also explain the causal relationship between them. Here, we analyzed the dependence structure for several bivariate and multivariate ecological, community and biogeochemical datasets. In addition to a copula based \nameref{Model_selection}, we also carried out a \nameref{NPA} with three different statistics to verify our model selection based results.

>>>>

Though a few examples have been found which shows copula approach to model dependencies in bioinformatics [@Kim2008], medical research [@Emura2016] or a short period study of intersite dependence of rainfall data [@Serinaldi2008], the multivariate copula approach still, we believe, remains unexplored in ecology or related field and thus have potential scope to better capture the evolution of ecological time series data. So, in ecological perspective, when we find a dominantly lower (upper) tail dependence structure, it means both incidence are rare (abundant) synchronously. If any one of them be environmental variable and the other is an observable (like abundance of a species) then it can also explain the causal relationship between them. Here, we analyzed the dependence structure for several bivariate and multivariate ecological, community and biogeochemical datasets. In addition to a copula based \nameref{Model_selection}, we also carried out a \nameref{NPA} with three different statistics to verify our model selection based results.
